\documentclass[10pt,a4paper, twoside]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[font=small]{caption}
\usepackage{wrapfig}
\usepackage{subfig}
\usepackage[a4paper,top=25mm,bottom=25mm]{geometry}
\author{Philipp Weder}
\date{}





% packages for layout
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\fancyhead[LE, RO]{\textit{\nouppercase{\leftmark}}}
\fancyhead[RE, LO]{\thepage}

%section titles
\usepackage{titlesec}


\titleformat{\section}
  {\centering\Large\scshape}{\thesection. }{1em}{}
  
\titleformat{\subsection}
  {\centering\large\scshape}{\thesubsection. }{1em}{}
  
\titleformat{\subsubsection}
  {\centering\scshape}{\thesubsubsection. }{1em}{}


%roman enumeration
\renewcommand\labelenumi{(\roman{enumi})}
\renewcommand\theenumi\labelenumi
\numberwithin{equation}{section}

% font
%\usepackage{pxfonts}

% bibliography
\usepackage[style=ieee, sorting = nty, backend = biber]{biblatex}
\bibliography{report.bib}
\usepackage{csquotes}

% environments
% theorem
\theoremstyle{plain}
\newtheorem{theorem}{Theorem}

% corollary
\theoremstyle{plain}
\newtheorem{corollary}[theorem]{Corollary}

% lemma
\theoremstyle{plain}
\newtheorem{lemma}[theorem]{Lemma}

% remark
\theoremstyle{remark}
\newtheorem*{remark}{Remark}
% definition
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
% example
\theoremstyle{definition}
\newtheorem{example}{Example}
% proposition
\theoremstyle{plain}
\newtheorem{proposition}[theorem]{Proposition}


\theoremstyle{plain}
\newtheorem{condition}[theorem]{Condition}


% additional packages
\usepackage{appendix}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{tikz}

\newcommand{\N}{\mathbb{N}}
\newcommand{\M}{\mathcal{M}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\h}{\mathcal{H}}
\newcommand{\K}{\mathcal{K}}
\DeclareMathOperator{\Skew}{Skew}
\DeclareMathOperator{\id}{id}
\newcommand{\so}{\mathfrak{so}}
\newcommand{\REF}{\mathrm{ref}}
\newcommand{\spr}{\textsc{SPr4}}
\DeclareMathOperator{\dist}{dist}
\DeclareMathOperator{\SO}{SO}
\DeclareMathOperator{\sgn}{sgn}
\DeclareMathOperator{\Aut}{Aut}
\DeclareMathOperator{\diag}{diag}
\newcommand{\chroexp}{\overset{\longrightarrow}{\exp}}
\DeclareMathOperator{\re}{Re}
\DeclareMathOperator{\Span}{span}
\newcommand{\dd}[1]{\mathrm{d}#1}
\DeclareMathOperator{\ad}{ad}
\newcommand{\T}{\mathcal{T}}
\newcommand{\strokes}{\dot{H}^{1}_{\sharp}(J, \R^4)}


\begin{document}
\thispagestyle{plain}

\begin{center}
   \vspace*{1cm} 

   \Huge
   \textsc{Parking 4-sphere swimmer}
   
  \vspace{0.25cm}
   \Large
   \textsc{Energy minimizing strokes}
   \vspace{1.5cm}
   
   Bachelor Thesis
   \vspace{1cm}
    \normalsize
    
    Submitted by\\
    \vspace{2em}
    \textsc{Philipp Weder}\\
    ETH Zürich\\
    Sonnenstrasse 12a\\
    9434 Au\\
    Switzerland\\
    \vspace{2em}
    supervised by\\
    \vspace{2em}
    \begin{minipage}[t]{0.4\textwidth}
    \begin{center}
    \textsc{Prof. Dr. François Alouges}\\
    Ecole Polytechnique,\\
    route de Saclay,\\
    91128 Palaiseau Cedex,\\
    France
    \end{center}
    \end{minipage}
    \begin{minipage}[t]{0.4\textwidth}
    \begin{center}
    \textsc{Dr. Aline Lefebvre-Lepot}\\
    Ecole Polytechnique,\\
    route de Saclay,\\
    91128 Palaiseau Cedex,\\
    France
    \end{center}
    \end{minipage}

    \vspace{2em}
    co-supervised by\\
    \vspace{2em}
    \textsc{Prof. Dr. Habib Ammari}\\
    ETH Zürich,\\
    Rämistrasse 101,\\
    8092 Zürich,\\
    Switzerland
    
    
\end{center}
  \vspace{1cm}
    
    \begin{abstract}
    This thesis is about the parking 4-sphere swimmer (\spr). This is a low-Reynolds number swimmer able to move in all of $3d$ space composed of four balls of equal radii. The four balls can move along the four axes passing through the four vertices of a tetrahedron and its midpoint.The governing dynamical system is presented and its geometric structure is displayed. Then we show that, in the first order range of small strokes, optimal periodic strokes are the sum of two elliptical strokes, i.e. curves of the form $t \in [0, 2 \pi] \mapsto \cos(t) u_1 + \sin(t) v_1 + \cos(2t) u_2 + \sin(2 t) v_2$ for suitable vectors $u_1, v_1, u_2, v_2 \in \R^4$, where the second mode vanishes in a special case. Then, the Stokes-induced governing dynamics is further simplified in the limit of very long arms, which allows the explicit statement of all the involved parameters in terms of the swimmer's geometry. 
    \end{abstract}

\newpage
\section*{Acknowledgements}
\input{acknowledgements}

\newpage
\setcounter{tocdepth}{2}
\tableofcontents

\newpage

\section{Introduction}
\input{introduction}

\section[Modeling]{Modeling of the control problem}
\input{modeling}

\section{Symmetries}
\input{symmetries}

\section{The small strokes regime}
\input{small_strokes}

\section{Energy minimizing strokes}
\input{optimization}

\section{The long arms approximation}
\input{sec_longarms.tex}
% \newpage
\section{Numerics}
\input{numerics}

\section{Conclusion and outlook}
\input{conclusion_and_outlook.tex}

\section{Appendix}
\input{appendix_report.tex}
\newpage

\printbibliography[title = Bibliography]



\end{document}